Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-19 WSSSPE3/report/WSSSPE3_review.tex
added nice TeX\LaTeX symbols

Turk then moved onto various different definitions of sustainability. His
favorite one was ``keeping up with bug reports,'' where even if no new features
were added, the software remains sustainable. Another definition of
sustainability Turk mentioned was ``adding of new features,'' or ``maintaining the
software for a long period of time'' such as the cases of TeX or LaTeX with
community help. A notion Turk heard often at supercomputing conferences was that
sustainable software ``continues to work on new architectures.'' Yet another
metric was ``people continuing to be able to learn how to use and apply the
software.'' A funder Turk heard talked about sustainability as ``continuing to get
funded.'' Turk also recalled that Greg Wilson, among others, said in WSSSPE1.1
that his view of sustainable software was software that ``continued to give the
same results over time.'' A last measure of sustainability Turk presented was
``the ability to transition between different people developing and using a piece
of software.''

>>>>

Turk then moved onto various different definitions of sustainability. His
favorite one was ``keeping up with bug reports,'' where even if no new features
were added, the software remains sustainable. Another definition of
sustainability Turk mentioned was ``adding of new features,'' or ``maintaining the
software for a long period of time'' such as the cases of \TeX\ or \LaTeX\ with
community help. A notion Turk heard often at supercomputing conferences was that
sustainable software ``continues to work on new architectures.'' Yet another
metric was ``people continuing to be able to learn how to use and apply the
software.'' A funder Turk heard talked about sustainability as ``continuing to get
funded.'' Turk also recalled that Greg Wilson, among others, said in WSSSPE1.1
that his view of sustainable software was software that ``continued to give the
same results over time.'' A last measure of sustainability Turk presented was
``the ability to transition between different people developing and using a piece
of software.''
